Validated Model Counting Data \\ Version of \today

### 2023-03-01 doc/mc-data.tex
Start on conference paper

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=3000000000,
      legend style={at={(0.30,0.98)}},
      legend cell align={left},
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=001,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000, 1e10}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$,$10^{10}$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-failure}
    \input{data-formatted/time+defining-success}
    \legend{
      \scriptsize \textsf{Limit exceeded},
      \scriptsize \textsf{Validated},
    }
 \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}

>>>>

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=3000000000,
      legend style={at={(0.30,0.98)}},
      legend cell align={left},
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=0.01,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000, 1e10}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$,$10^{10}$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-failure}
    \input{data-formatted/time+defining-success}
    \legend{
      \scriptsize \textsf{Limit exceeded},
      \scriptsize \textsf{Validated},
    }
 \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}
